---
title: "ggplot Notebook"
output: html_notebook
---

ggplot2 is a data visualization package. We can create different types of graphs and charts using the ggplot() in the ggplot2 library.

We create a base layer by specifying the data.
A layer combines data, aesthetic mapping, a geom (geometric object), a stat (statistical transformation), and a position adjustment. Typically, we create layers using a geom_ function



We start by loading the ggplot2 library

```{r}
require("ggplot2")
```




Load cars dataset in a dataframe

```{r}
#plot(cars)

df_cars <- cars
```



*********** - SCATTERPLOT - ***************



Create a scatterplot of speed v/s distance

```{r}
g <- ggplot(df_cars, aes(x=speed, y=dist)) + geom_point()
g
```



We could also zoom into a section of the graph by mentioning the coordinates

```{r}
g_new <- g + coord_cartesian(xlim = c(10,15), ylim = c(25,50))
g_new
```




************ - HISTOGRAM - ****************



Load mtcars dataset in a dataframe

```{r}
df_cars <- mtcars
```

Create a basic histogram of the data with weight on x-axis, and a count of weight on y-axis

```{r}
ggplot(df_cars, aes(x=wt)) + geom_histogram()
```

We could specify the bin-width, the outline color and the fill color of the histogram

```{r}
g <- ggplot(df_cars, aes(x=wt)) + geom_histogram(binwidth = 0.5, color="blue", fill="white")
g
```



If we want to plot the mean of the vertical distribution, we could draw a vertical line

```{r}
g + geom_vline(aes(xintercept=mean(wt)), color="red", linetype="dashed", size=1)

```


We could also stack up another layer showing the density of the data on top of this histogram. Note that the density (pdf or pmf) always sums up to 1

```{r}
ggplot(df_cars, aes(x=wt)) +
  geom_histogram(binwidth = 0.5, aes(y = ..density..), 
                 alpha=0.3, color="blue", fill="white") +
  geom_density(alpha=0.2, fill="red")
```

